The Globular Cluster System of the Auriga Simulations

### 2019-02-11 AurigaGCS.tex
Added KS test figures

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[T. L. R. Halbesma et al.]{\parbox[t]{\textwidth}{
    Timo L. R. Halbesma$^{1}$\thanks{E-mail: Halbesma@MPA-Garching.MPG.DE},
    Philipp Busch$^{1}$,
    Wilma Trick$^{1}$,
    Robert J. J. Grand$^{1}$, 
    Volker Springel$^{1}$, 
    Facundo A. G\'{o}mez$^{2,3}$, 
    Federico Marinacci$^{4,5}$,
    R\"{u}diger Pakmor$^{1}$, 
    Simon D. M. White$^{1}$
} \vspace{10pt} \\
$^{1}$ Max-Planck-Institut f\"ur Astrophysik, Postfach 1317, D-85741 Garching, Germany \\
$^{2}$ Instituto de Investigaci\'{o}n Multidisciplinar en Ciencia yTecnolog\'{i}a, 
    Universidad de La Serena, Ra\'{u}l Bitr\'{a}n 1305, La Serena, Chile \\
$^{3}$ Departamento de F\'{i}sica y Astronom\'{i}a, Universidad de La Serena, Av.
    Juan Cisternas 1200 N, La Serena, Chile \\
$^{4}$ Department of Physics, Kavli Institute for Astrophysics and Space Research,
    MIT, Cambridge, MA 02139, USA \\
$^{5}$ Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge,
    MA 02138, USA \\
}

@@

% Abstract of the paper
\begin{abstract}
We investigate whether the galaxy formation model used for the Auriga simulations 
can produce a realistic globular cluster population at redshift zero. We compare
properties of the simulated star particles in the Auriga haloes with
catalogues of observations of the Milky Way globular cluster population available
in the literature. We find that the Auriga simulations produce sufficient mass
at radii and metallicities that are typical for the MW GCS, although we observe
a varying mass-excess for the different $r_{\text{gal}}$-[Fe/H] bins. This implies
different values for the combined product of the bound cluster formation efficiency
and the globular cluster disruption rate. We investigate wether these differences
could result from formation insitu vs. accreted star particles. We find ...
\end{abstract}

@@

\citet{2005MNRAS.364..367D}: ``The radial profile of the stellar halo and metal-poor globular
clusters of the Milky Way suggest that these components formed in rare early peaks above $2.5 \sigma$ at redshift above 10. ''

\citet{2017MNRAS.465.3622R}: ``GCs among oldest astrophysical objects. GCs form in the early Universe in highest density peaks \citep[e.g.][]{2005MNRAS.364..367D, 2009ApJ...706L.192B}''

\begin{itemize}
    \item ``Hence, they witness most of the formation and evolution processes of galaxies, and can be used to probe them'' \citep{2006ARA&A..44..193B}
    \item ``colour bimodality, blue and red clusters \citep[e.g.][]{1985ApJ...293..424Z, 1999AJ....118.1526G, 2001AJ....121.2974L, 2006ApJ...639...95P}
    \item ``blue metal-poor (with distribution peaking at [Fe/H] $\approx -1.5$ for the Milky Way), no sign of rotation as a population (..) more metal-rich (peak at [Fe/H] $\approx -0.5$ in the Milky  Way) more spatially concentrated and rotating with the galaxy.'' \citep{1996AJ....112.1487H}
\end{itemize}

\todo[inline]{Paragraph: ``Bimodality suggests two formation mechanisms''. In-situ vs. Accreted}
\begin{itemize}
    \item ``Blue clusters from in early Universe in galaxies that merge later. In (wet) merger process starbursts generate red population \cite{1992ApJ...384...50A, 1987nngp.proc...18S}''
    \item ``\citet{1997AJ....113.1652F} propose instead that blue globulars form when the protogalaxy itself collapses, in a metal-poor and turbulence media. The red population would form later, once the galactic disc has settled. The formation of globular clusters would then be a multiphase process, with the first phase being interrupted possibly by cosmic reionization \citep{2002MNRAS.333..383B}.''
    \item ``\citet{2005ApJ...623..650K, 2014ApJ...796...10L} advocate
that major mergers are at the origin of both sub-populations: blue
clusters form during early mergers (z > 4) while the red ones appear
in mergers at lower redshifts (even after z = 1). Although, this
scenario, combined with star formation enhancement in mergers,
seems appropriate in dense galactic environment leading to the
assembly of massive elliptical galaxies, like in the Virgo Cluster
as tested by \citet{2014ApJ...796...10L}, it does not apply to Milky Way-
like systems where no recent major merger took place (Wyse 2001;
Deason et al. 2013; Ruchti et al. 2014, 2015).
\item ``\citet{1998ApJ...501..554C} argue that red clusters form in situ while the blue ones are accreted, either via merging satellite galaxies, or by tidal capture of the clusters themselves \citep[see also][]{2013ApJ...762...39T}.''
\end{itemize}

Dark Matter - GC connection

\todo[inline]{Paragraph: scientific motivation}
\begin{itemize}
    \item The star formation model implemented in the Auriga simulations is capable of producing a suite/population of realistic Milky Way-like galaxies at redshift zero.
    \item (However) State of the art simulations still face numerical restrictions that requires a subgrid approach to star formation and feedback because individual stars (and their evolution) cannot yet be accounted for. Star formation thus occurs in a heuristic/probabilistic fashion for gas cells that fulfill some star formation criterion. The star particles enrich the gas with metals and energy, both according to pre-defined/pre-calculated yields for specific feedback processes (supernova type I and II, strong stellar winds of asymptotic giant branch stars, ). In addition, black holes are seeded in eligible haloes to account for feedback associated with an active galactic nucleus.
    \item The end-result of the star formation model is the production of simulated Milky Way-like galaxies. Therefore the question naturally arises whether or not the Auriga simulations are also capable of faithfully producing a globular cluster population as observed in the Milky Way.
    \item Globular cluster formation in cosmological zoom simulations is very interesting for two reasons. First of all, extragalactic observations typically show the integrated properties of globular clusters rather than that of the individual stars within the clusters. Moreover, the typical mass scale of globular clusters is comparable to the numerical (mass) resolution of cosmological zoom simulations. The detailed small scale physics that is at play for real world globular clusters appears in observations as the combined effect of the $10^{3-6}$ M\Sun, compared to a mass resolution of $10^{3-5}$ M\Sun for the Auriga simulations. Globular clusters can therefore serve as an ultimate test to the star formation model that is implemented in the numerical simulations. Secondly, cosmological zoom simulations provide an accurate recording of the full and detailed merger history of the simulated galaxy. This is important because theoretical paradigms for globular cluster formation in the literature know two distinct classes of GCs that are separated by their exact formation sites: an in-situ versus an accreted population. Cosmological zoom simulations are uniquely allow for an investigation into globular cluster formation with particular focus on the in-situ and accreted populations.
\end{itemize}

\todo[inline]{Paragraph: previous work / work of other groups}
This goes before the GC formation mechanism paragraph.
\begin{itemize}
\item Origin of the Milky Way globular clusters \citep{2017MNRAS.465.3622R}
\item GCs in FIRE \citep{2018MNRAS.474.4232K}
\item EMOSAICS project \citep{2018MNRAS.475.4309P}
\item Origin of GC bimodality? \citep{2018MNRAS.479..200F}
\item \textit{GAIA} DR2: GC kinematics \citep{2018A&A...616A..12G}, Dating GC Tidal Disruption \citep{2018ApJ...859L..13B}
\item GC in N-body simulation \citep{2018ApJ...861...69C}
\item Tangentially related? role of GC mass evolution on stream properties \citep{2018MNRAS.474.2479B}
\item GC formation from dwarfs to giants \citep{2018MNRAS.480.2343C}
\item GC contribution to EOR \citep{2018MNRAS.479..332B}
\item Early Universe supermassive star / GC formation \citep{2018MNRAS.478.2461G}
\item GC formation in cold filaments \citep{2018ApJ...861..148M}
\item GC formation in high-redshift dwarf galaxies \citep{2018MNRAS.477..480Z}
\item GCs in MW outer region \citep{2017arXiv170804542P}
\item Impact of the Cutoff of the Cluster Initial Mass Function \citep{2018arXiv181001888C}
\item Metallicity gradients in the globular cluster systems of early-type galaxies: in situ and accreted components \citep{2018MNRAS.479.4760F}
\item Globular clusters in M31, Local Group, and external galaxies \citep{2016IAUS..317..120L}
\item Globular Clusters Formed within Dark Halos I: present-day abundance, distribution and kinematics \citep{2019MNRAS.482..219C}
\item The mass of the Milky Way from satellite dynamics \citep{2018arXiv180810456C}
\item Globular cluster formation and evolution in the context of cosmological galaxy assembly: open questions \citep{2018RSPSA.47470616F}
\item The kinematics of globular clusters systems in the outer halos of the Aquarius simulations \citep{2016A&A...592A..55V}
\item Star Cluster Formation in Cosmological Simulations \citep{2017ApJ...834...69L, 2018ApJ...861..107L, 2018arXiv181011036L}
\item A systematic analysis of star cluster disruption by tidal shocks -- I. Controlled N-body simulations and a new theoretical model \citep{2018arXiv181200014W}
\item Spatial mixing of binary stars in multiple-population globular clusters \citep{2018MNRAS.tmp.3147H}
\item Star Clusters Across Cosmic Time \citep{2018arXiv181201615K}
\item Kinematics of Subclusters in Star Cluster Complexes: Imprint of their Parental Molecular Clouds \citep{2018arXiv181201858F}
\item Investigating the population of Galactic star formation regions and star clusters within a Wide-Fast-Deep Coverage of the Galactic Plane  \citep{2018arXiv181203025P}
% TODO: last checked arXiv Dec 15, 2018
\end{itemize}

\todo[inline]{Paper outline}
We summarise the relevant characteristics of the Auriga simulations in 
section~\ref{sec:auriga}, followed by a summary of the observations of the
Milky Way (MW) globular cluster system (GCS) in section~\ref{sec:observations}
that we use to compare our simulations to in section~\ref{sec:results}. We
discuss our findings in section~\ref{sec:discussion} to come to our conclusions 
in section~\ref{sec:conclusions}.

@@

\todo[inline]{
``The diversity in morphological properties of these simulated galaxies reflects
the stochasticity inherent to the process of galaxy formation and evolution 
\citep[e.g.][]{2005ApJ...635..931B, 2010MNRAS.406..744C, 2010ApJ...708.1398T}.''
}

\subsection{Definition of stellar halo}
\todo[inline]{Possibly also relevant here. See \citet{2018arXiv180407798M}.}

\subsection{Definition of accreted and in-situ component}
\todo[inline]{Possibly also relevant here. See \citet{2018arXiv180407798M}.}

\section{Relevant observational data}
\label{sec:observations}
The galaxy formation model implemented for the Auriga simulations produces
realistic spiral galaxies at redshift zero. Therefore we aim to compare the
simulations to the globular cluster systems of the spiral galaxies in the 
Local Group (i.e. the Milky Way and Andromeda galaxy or M31). Here we summarise 
the relevant data available in the literature.

\subsection{Milky Way: Harris catalogue}
\label{sec:harris}
\citet[][2010 edition; hereafter H96]{1996AJ....112.1487H} provides a fairly
up-to-date, comprehensive catalogue of the Milky Way globular cluster system and
contains properties of 157 globular clusters. The catalogue is believed to be 
roughly 90\% complete. The relevant data fields that we use from H96 are the 
metallicity [Fe/H], galactocentric radius $r_{\text{gal}}$, and absolute magnitude 
in the V-band $M_V$. 
\todo[inline]{
We use the latter to calculate a mass-estimate by assuming
$M_{V,\odot}=4.83$ and a mass to light ratio $M/L_V = 1.7$~M/L$_{\odot}$ 
(the mean for MW clusters McLaughlin \& van der Marel 2005). 
}

In Fig.~\ref{fig:MW-RgcFeH} we show a two-dimensional mass-weighted distribution,
splitting the data up in bins of both radius and metallicity. Later on we 
investigate whether the star formation model implemented for the Auriga simulations 
can produce a sufficient total mass in globular cluster candidates at the right
values of radius, metallicity, and radius-metals, see Sec.~\ref{sec:RgcFeH}

\begin{figure}
    \includegraphics[width=\columnwidth]
        {{MW_M31_RgcFeH_HistogramMassWeighted_Harris1996ed2010data}.png}
    \caption{
        Mass-weighted r$_{\text{gc}}$-[Fe/H] distribution of
        151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H}, which
        is 98.19 \% of the total MW GCS mass.
        \label{fig:MW-RgcFeH}
    }
\end{figure}

\subsection{Milky Way: VandenBerg catalogue}
\label{sec:vandenberg}
\citet[][hereafter V13]{2013ApJ...775..134V} used photometric data to obtain 
[Fe/H] measurements and age-estimates for 55 globular clusters in the Milky Way.
The mean value of the age-estimates in this data set is $11.9 \pm 0.1$ Gyr and the
dispersion is 0.9 Gyr. Furthermore, only one of the 55 GC age-estimates is
below 10 Gyr.

@@

\subsection{Andromeda: Caldwell catalogue}
\label{sec:m31}
\citet[][, hereafter C11]{2011AJ....141...61C} studied globular clusters in the
Andromeda galaxy. The relevant fields in this data set are the age, metallicities,
and absolute visual magnitude.
\todo[inline]{
`For M31 GC masses we combine the catalogues of Caldwell et al. (2011, using the 
given masses) and Huxor et al. (2014, again assuming $M/L_V = 1.7$~M/L$_{\odot}$, 
e.g. Strader, Caldwell \& Seth 2011).'
}
For M31 we find an age distribution with a mean value of 10.8$\pm 10.8$~Gyr and a 
dispersion of 2.3~Gyr. Furthermore, 27 GCs have age-estimates below 10~Gyr, and
the minimum age is 4.8~Gyr. Perhaps an age cut of 6~Gyr would would be more 
appropriate for M31, see Fig.~\ref{fig:MW-M31-age}.

@@

\todo[inline]{
Furthermore, we supplement observational data of globular clusters in M31 with 
\citet{2014MNRAS.442.2165H, 2014MNRAS.442.2929V}
}

\section{Results}
\label{sec:results}
We investigate globular cluster candidates in the Auriga simulations using an age
cut to select of stars that formed at a lookback time greater than $10$~Gyr. We 
chose this particular value because the mean age-estimate of the $55$ in V13 is
$11.9\pm0.1$~Gyr with a dispersion of $0.8$~Gyr, and only one observed globular 
cluster falls below this selection criterion.

In Sec.~\ref{sec:metallicity} we investigate the metallicity distribution of the
GC candidates, in Sec.~\ref{sec:spatial} we show the distribution of galactocentric
radii of the globular cluster candidates within the Auriga simulations, and we 
combine both in Sec.~\ref{sec:RgcFeH}. We continue our analysis with a deeper 
analysis of the properties of the proto-galaxies at times of birth of the accreted 
globular cluster population in Sec.~\ref{sec:birth-properties-of-accreted-gc-candidates}

\subsection{Metallicity distribution}
\label{sec:metallicity}
\todo[inline]{
Can the Auriga simulations produce star particles of $>10$~Gyr (GC candidates) 
with a metallicity distribution that is consistent with the MW GCS?
}

In Fig.~\ref{fig:FeH} we show a mass-weighted metallicity distribution of star 
particles in the Auriga simulations. We show the median value of all Auriga 
haloes for all stars (orange dotted lines) and globular cluster candidates 
orange solid). The latter sub set is further split up between stars that formed 
in-situ (red solid), and those that were accreted (blue solid). The shaded regions 
indicate the $1\sigma$ interval. The MW GCS is shown in purple and that of M31 
in pink. We use the same bin sizes for the simulations as for the observations, 
explicitly plotted for the observed profiles.

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMFeH_noStepsMid-trim}.png}
    \caption{
        Mass-weighted metallicity distribution of star particles in the Auriga 
        simulations. We show the median value of all Auriga haloes for all
        stars (orange dotted) and globular cluster candidates (i.e. stars with 
        age $>$~10~Gyr; orange solid). The latter sub set is further split up
        between stars that formed in-situ (red solid), and those that were accreted
        (blue solid). Shaded regions indicate the $1\sigma$ interval. The MW GCS
        is shown in purple and that of M31 in pink. We use the same bin sizes
        for the simulations as for the observations, explicitly plotted for the
        observed profiles.
        \label{fig:FeH}
    }
\end{figure}

We find that the metallicity range $-3 <$ [Fe/H] $< -1$ is only populated by 
star particles older than ten Gyr, while [Fe/H] $> -1$ is dominated by star 
particles younger than 10~Gyr (with a difference of two orders of magnitude). 
Furthermore, the old accreted star particles contribute most significantly to 
the range $-3 <$ [Fe/H] $< -1$, and the contribution of the old in-situ star
particles at these metallicities declines steeper with declining metallicity 
than the old accreted population. The old in-situ population provides the 
dominant contribution of the old population for [Fe/H] $> -1$.

>>>>

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[T. L. R. Halbesma et al.]{\parbox[t]{\textwidth}{
    Timo L. R. Halbesma$^{1}$\thanks{E-mail: Halbesma@MPA-Garching.MPG.DE},
    Robert J. J. Grand$^{1}$, 
    Volker Springel$^{1}$, 
    Facundo A. G\'{o}mez$^{2,3}$, 
    Federico Marinacci$^{4,5}$,
    R\"{u}diger Pakmor$^{1}$, 
    Wilma Trick$^{1}$,
    Philipp Busch$^{1}$,
    Simon D. M. White$^{1}$
} \vspace{10pt} \\
$^{1}$ Max-Planck-Institut f\"ur Astrophysik, Postfach 1317, D-85741 Garching, Germany \\
$^{2}$ Instituto de Investigaci\'{o}n Multidisciplinar en Ciencia yTecnolog\'{i}a, 
    Universidad de La Serena, Ra\'{u}l Bitr\'{a}n 1305, La Serena, Chile \\
$^{3}$ Departamento de F\'{i}sica y Astronom\'{i}a, Universidad de La Serena, Av.
    Juan Cisternas 1200 N, La Serena, Chile \\
$^{4}$ Department of Physics, Kavli Institute for Astrophysics and Space Research,
    MIT, Cambridge, MA 02139, USA \\
$^{5}$ Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge,
    MA 02138, USA \\
}

@@

% Abstract of the paper
\begin{abstract}
\todo[inline]{Ask SW whether I should ask Carlos Frenk and Adrian Jenkins for co-authorship}
We investigate whether the galaxy formation model used for the Auriga simulations 
can produce a realistic globular cluster population at redshift zero. We compare
properties of the simulated star particles in the Auriga haloes with
catalogues of observations of the Milky Way globular cluster population available
in the literature. We find that the Auriga simulations produce sufficient mass
at radii and metallicities that are typical for the MW GCS, although we observe
a varying mass-excess for the different $R_{\text{GC}}$-[Fe/H] bins. This implies
different values for the combined product of the bound cluster formation efficiency
and the globular cluster disruption rate. We investigate wether these differences
could result from formation insitu vs. accreted star particles. We find ...
\end{abstract}

@@

\begin{itemize}
    \item \citet{2005MNRAS.364..367D}: ``The radial profile of the stellar halo
    and metal-poor globular clusters of the Milky Way suggest that these components 
    formed in rare early peaks above $2.5 \sigma$ at redshift above 10. ''

    \item \citet{2017MNRAS.465.3622R}: ``GCs among oldest astrophysical objects.
    GCs form in the early Universe in highest density peaks
    \citep[e.g.][]{2005MNRAS.364..367D, 2009ApJ...706L.192B}''

    \item ``Hence, they witness most of the formation and evolution processes
    of galaxies, and can be used to probe them'' \citep{2006ARA&A..44..193B}
\end{itemize}

\todo[inline]{Paragraph: scientific context / state of the field: briefly summarise
    previous work and references work of other groups}
\begin{itemize}
\item Origin of the Milky Way globular clusters \citep{2017MNRAS.465.3622R}
\item GCs in FIRE \citep{2018MNRAS.474.4232K}
\item EMOSAICS project \citep{2018MNRAS.475.4309P}
\item GC-DMhalo connection \citep{2017MNRAS.472.3120B}
\item Origin of GC bimodality? \citep{2018MNRAS.479..200F}
\item \textit{GAIA} DR2: GC kinematics \citep{2018A&A...616A..12G}
\item Dating GC Tidal Disruption \citep{2018ApJ...859L..13B}
\item GC in N-body simulation \citep{2018ApJ...861...69C}
\item (Role of GC mass evolution on stream properties \citep{2018MNRAS.474.2479B})
\item GC formation from dwarfs to giants \citep{2018MNRAS.480.2343C}
\item (GC contribution to EOR \citep{2018MNRAS.479..332B})
\item Early Universe supermassive star / GC formation \citep{2018MNRAS.478.2461G}
\item GC formation in cold filaments \citep{2018ApJ...861..148M}
\item GC formation in high-redshift dwarf galaxies \citep{2018MNRAS.477..480Z}
\item GCs in MW outer region \citep{2017arXiv170804542P}
\item Impact of the Cutoff of the Cluster Initial Mass Function \citep{2018arXiv181001888C}
\item Metallicity gradients in the globular cluster systems of early-type galaxies: in situ and accreted components \citep{2018MNRAS.479.4760F}
\item Globular clusters in M31, Local Group, and external galaxies \citep{2016IAUS..317..120L}
\item Globular Clusters Formed within Dark Halos I: present-day abundance, distribution and kinematics \citep{2019MNRAS.482..219C}
\item (The mass of the Milky Way from satellite dynamics \citep{2018arXiv180810456C})
\item Globular cluster formation and evolution in the context of cosmological galaxy assembly: open questions \citep{2018RSPSA.47470616F}
\item The kinematics of globular clusters systems in the outer halos of the Aquarius simulations \citep{2016A&A...592A..55V}
\item Star Cluster Formation in Cosmological Simulations \citep{2017ApJ...834...69L, 2018ApJ...861..107L, 2018arXiv181011036L}
\item (A systematic analysis of star cluster disruption by tidal shocks - I. Controlled N-body simulations and a new theoretical model \citep{2018arXiv181200014W})
\item Spatial mixing of binary stars in multiple-population globular clusters \citep{2018MNRAS.tmp.3147H}
\item Star Clusters Across Cosmic Time \citep{2018arXiv181201615K}
\item Kinematics of Subclusters in Star Cluster Complexes: Imprint of their Parental Molecular Clouds \citep{2018arXiv181201858F}
\item Investigating the population of Galactic star formation regions and star clusters within a Wide-Fast-Deep Coverage of the Galactic Plane  \citep{2018arXiv181203025P}
\item Globular cluster number density profiles using \textit{Gaia} DR2 \citep{2019arXiv190108072D}
% TODO: last checked arXiv Jan 27, 2018
\end{itemize}

\todo[inline]{Paragraph, narrowing open questions in GC research down to formation,
    possibly ``Bimodality suggests two formation mechanisms''. In-situ 
    formation vs. accretion in hierarchical build-up of galaxies naturally produces 
    two populations of globular cluster.}
\begin{itemize}
    \item ``colour bimodality, blue and red clusters \citep[e.g.][]{1985ApJ...293..424Z, 1999AJ....118.1526G, 2001AJ....121.2974L, 2006ApJ...639...95P}
    \item ``blue metal-poor (with distribution peaking at [Fe/H] $\approx -1.5$ for the Milky Way), no sign of rotation as a population (..) more metal-rich (peak at [Fe/H] $\approx -0.5$ in the Milky  Way) more spatially concentrated and rotating with the galaxy.'' \citep{1996AJ....112.1487H}
    \item ``Blue clusters from in early Universe in galaxies that merge later. In (wet) merger process starbursts generate red population \cite{1992ApJ...384...50A, 1987nngp.proc...18S}''
    \item ``\citet{1997AJ....113.1652F} propose instead that blue globulars form when the protogalaxy itself collapses, in a metal-poor and turbulence media. The red population would form later, once the galactic disc has settled. The formation of globular clusters would then be a multiphase process, with the first phase being interrupted possibly by cosmic reionization \citep{2002MNRAS.333..383B}.''
    \item ``\citet{2005ApJ...623..650K, 2014ApJ...796...10L} advocate
that major mergers are at the origin of both sub-populations: blue
clusters form during early mergers (z > 4) while the red ones appear
in mergers at lower redshifts (even after z = 1). Although, this
scenario, combined with star formation enhancement in mergers,
seems appropriate in dense galactic environment leading to the
assembly of massive elliptical galaxies, like in the Virgo Cluster
as tested by \citet{2014ApJ...796...10L}, it does not apply to Milky Way-
like systems where no recent major merger took place (Wyse 2001;
Deason et al. 2013; Ruchti et al. 2014, 2015).
\item ``\citet{1998ApJ...501..554C} argue that red clusters form in situ while the blue ones are accreted, either via merging satellite galaxies, or by tidal capture of the clusters themselves \citep[see also][]{2013ApJ...762...39T}.''
\end{itemize}

\todo[inline]{Paragraph: narrow the scientific motivation down to the scope of 
    this particular work}
\begin{itemize}
    \item The star formation model implemented in the Auriga simulations is capable of producing a suite/population of realistic Milky Way-like galaxies at redshift zero.
    \item (However) State of the art simulations still face numerical restrictions that requires a subgrid approach to star formation and feedback because individual stars (and their evolution) cannot yet be accounted for. Star formation thus occurs in a heuristic/probabilistic fashion for gas cells that fulfill some star formation criterion. The star particles enrich the gas with metals and energy, both according to pre-defined/pre-calculated yields for specific feedback processes (supernova type I and II, strong stellar winds of asymptotic giant branch stars, ). In addition, black holes are seeded in eligible haloes to account for feedback associated with an active galactic nucleus.
    \item The end-result of the star formation model is the production of simulated Milky Way-like galaxies. Therefore the question naturally arises whether or not the Auriga simulations are also capable of faithfully producing a globular cluster population as observed in the Milky Way.
    \item Globular cluster formation in cosmological zoom simulations is very interesting for two reasons. First of all, extragalactic observations typically show the integrated properties of globular clusters rather than that of the individual stars within the clusters. Moreover, the typical mass scale of globular clusters is comparable to the numerical (mass) resolution of cosmological zoom simulations. The detailed small scale physics that is at play for real world globular clusters appears in observations as the combined effect of the $10^{3-6}$ M\Sun, compared to a mass resolution of $10^{3-5}$ M\Sun for the Auriga simulations. Globular clusters can therefore serve as an ultimate test to the star formation model that is implemented in the numerical simulations. Secondly, cosmological zoom simulations provide an accurate recording of the full and detailed merger history of the simulated galaxy. This is important because theoretical paradigms for globular cluster formation in the literature know two distinct classes of GCs that are separated by their exact formation sites: an in-situ versus an accreted population. Cosmological zoom simulations uniquely allow for an investigation into globular cluster formation with particular focus on the in-situ and accreted populations.
\end{itemize}

\todo[inline]{Paragraph: Paper outline}
We summarise the relevant characteristics of the Auriga simulations in 
section~\ref{sec:auriga}, followed by a summary of the observations of the
Milky Way (MW) globular cluster system (GCS) in section~\ref{sec:observations}
that we use to compare our simulations to in section~\ref{sec:results}. We
discuss our findings in section~\ref{sec:discussion} to come to our conclusions 
in section~\ref{sec:conclusions}.

@@

\todo[inline]{
TODO: paraphrase ``The diversity in morphological properties of these simulated galaxies reflects
the stochasticity inherent to the process of galaxy formation and evolution 
\citep[e.g.][]{2005ApJ...635..931B, 2010MNRAS.406..744C, 2010ApJ...708.1398T}.''
}

\todo[inline]{Paragraph about Auriga's stellar haloes.
``The Auriga Stellar Haloes: Connecting stellar population properties with
accretion and merging history'' \citet{2018arXiv180407798M}
}

% \subsection{Definition of stellar halo}
% \todo[inline]{Possibly also relevant here. See \citet{2018arXiv180407798M}.}
% 
% 
% \subsection{Definition of accreted and in-situ component}
% \todo[inline]{Possibly also relevant here. See \citet{2018arXiv180407798M}.}

\section{Relevant observational data}
\label{sec:observations}
The galaxy formation model implemented for the Auriga simulations produces
realistic spiral galaxies at redshift zero. Therefore we aim to compare the
simulations to the globular cluster systems of the spiral galaxies in the 
Local Group (i.e. the Milky Way and Andromeda galaxy, M31). Here we summarise 
the relevant data available in the literature.

\subsection{Milky Way: Harris catalogue}
\label{sec:harris}
\citet[][2010 edition; hereafter H96]{1996AJ....112.1487H} provides a fairly
up-to-date catalogue of the Milky Way globular cluster system containing the
properties of 157 globular clusters. An additional 59 GCs have since been 
discovered, 2 of which by \citet{2018ApJ...863L..38R}. The authors also provide 
a comprehensive list of references to other discovery papers, and they predict 
that the Milky Way GCS contains an additional 30 undiscovered GCs that are 
obscured by the Galactic disk. Recently, \citet{2019arXiv190108574C} announced
the discovery of three new GCs, totalling to the MW GCS to 218. This would make
the Harris catalogue roughly 65\% complete. However, we do not use the properties 
of the more recently discovered GCs in our analysis.

The relevant data fields that we use from H96 are the metallicity [Fe/H],
galactocentric radius $R_{\text{GC}}$, and absolute magnitude in the V-band 
$M_V$. We use the latter to calculate mass-estimates by assuming $M_{V,\odot}=4.83$
and a mass to light ratio $M/L_V = 1.7$~M/L$_{\odot}$, the mean for MW clusters
\citep{2005ApJS..161..304M}.

\todo[inline]{Parse McLaughlin \& van der Marel data and calculate the mean $M/L_V$
\url{http://vizier.cfa.harvard.edu/viz-bin/VizieR-3?-source=J/ApJS/161/304/clusters}}

In Fig.~\ref{fig:MW-FeHRgc} we show the two-dimensional mass-weighted 
metallicity-radial distribution of the MW GCS. In Sec.~\ref{sec:FeHRgc} 
we investigate whether the star formation model implemented in the Auriga 
simulations can produce sufficient total mass in GC candidates in the same bins.

\begin{figure}
    \includegraphics[width=\columnwidth]
        {{MW_M31_RgcFeH_HistogramMassWeighted_Harris1996ed2010data}.png}
    \caption{
        Mass-weighted r$_{\text{gc}}$-[Fe/H] distribution of
        151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H}, which
        is 98.19 \% of the total MW GCS mass in the Harris catalog.
        \label{fig:MW-FeHRgc}
    }
\end{figure}

\subsection{Milky Way: VandenBerg catalogue}
\label{sec:vandenberg}
\citet[][hereafter V13]{2013ApJ...775..134V} used photometric data to obtain 
[Fe/H] measurements and age-estimates for 55 globular clusters in the Milky Way.
The mean value of the age-estimates in this data set is $11.9 \pm 0.1$~Gyr and 
the dispersion is 0.9~Gyr. Furthermore, only one of the 55 GC age-estimates is
below 10~Gyr. Therefore we define GC candidates in the Auriga simulations as
all star particles older than 10~Gyr in Sec.~\ref{sec:results}.

@@

\subsection{Andromeda: Caldwell catalogue}
\label{sec:m31}
\citet[][, hereafter C11]{2011AJ....141...61C} studied globular clusters in the
Andromeda (M31) galaxy. The relevant fields in this data set are the age, 
metallicities, and absolute visual magnitude.
\todo[inline]{
TODO: paraphrase ``For M31 GC masses we combine the catalogues of Caldwell et al. (2011, using the 
given masses) and Huxor et al. (2014, again assuming $M/L_V = 1.7$~M/L$_{\odot}$, 
e.g. Strader, Caldwell \& Seth 2011).''
}
For M31 we find an age distribution with a mean value of 10.8$\pm 10.8$~Gyr and a 
dispersion of 2.3~Gyr. Furthermore, 27 GCs have age-estimates below 10~Gyr, and
the minimum age is 4.8~Gyr.

TODO: (in discussion) Perhaps an age cut of 6~Gyr would would be more 
appropriate for M31, see Fig.~\ref{fig:MW-M31-age}.

@@

\todo[inline]{
TODO: paraphrase ``Furthermore, we supplement observational data of globular
clusters in M31 with \citet{2014MNRAS.442.2165H, 2014MNRAS.442.2929V}'', and
parse these data sets.
}

This text sits here just for debug purposes, just for now. We calculate the 
projected and `inferred' galactocentric radius from the observed coordinates.
\begin{align}
    \cos \theta & = \sin \delta_1 \sin \delta_2 +
        \cos \delta_1 \cos \delta_2 \cos \left( \alpha_1 - \alpha_2 \right),
\end{align}
where $(\alpha_1, \delta_1)$ are the right ascension and declination (in degrees,
converted to radians) of the centroid of M31 and $(\alpha_2, \delta_2)$ are the
observed coordinates of the globular cluster. The angle on the sky is converted
to a physical distance in kpc using the small angle approximation, i.e. 
$r_{\text{projected}} = \theta \cdot D_{\text{M31}}$. We adopt the values 
$(\alpha_1, \delta_1) = (0^{\text{h}}42^{\text{m}}44.3^{\text{s}}, 
+41^{\circ}16'9")$ (TODO: reference), and  $D_{\text{M31}} = 778$~kpc 
(TODO: reference).

% TODO: Deprojection, assuming all GCs lie in the plane of the sky, inclination 
% $12.5^{\circ}$

\section{Results}
\label{sec:results}
Through out the analysis we use six sub sets of star particles: \emph{all stars}, 
and \emph{old stars} (age $>10$~Gyr, GC candidates hereafter). Both sub sets are
further split up in (old) star particles that have formed \emph{in-situ} 
(bound to the most-massive halo/subhalo in the first snapshot that the star 
particle was recorded), and (old) \emph{accreted} star particles (i.e. those that 
have formed ex-situ and are bound to the most-massive halo/subhalo at $z=0$). 
We use an age threshold of 10~Gyr for GC candidates because the mean 
age-estimate of the $55$ MW GCs in V13 is $11.9\pm0.1$~Gyr with a dispersion of 
$0.8$~Gyr, and only one observed GC lies outside this range.

In Sec.~\ref{sec:metallicity} we investigate the metallicity distribution of the
GC candidates, in Sec.~\ref{sec:radial} we show the distribution of galactocentric
radii of the globular cluster candidates within the Auriga simulations, and we 
combine both in Sec.~\ref{sec:FeHRgc}. We continue our analysis with an investigation
of the properties of the proto-galaxies at times of birth of the accreted globular 
cluster population in Sec.~\ref{sec:birth-properties-of-accreted-gc-candidates}

\subsection{Metallicity distribution}
\label{sec:metallicity}
We investigate whether the star formation model implemented in the Auriga 
simulations is capable of producing sufficient mass in old star particles in 
each metallicity bin in comparison to the Milky Way and Andromeda globular 
cluster systems. In Fig.~\ref{fig:FeH} we show a mass-weighted metallicity 
distribution where the lines show the median value of all thirty Auriga level 4 
haloes for \emph{all stars} (orange dotted), \emph{old stars / GC candidates} 
(orange solid), \emph{old in-situ} stars (blue solid), and \emph{old accreted} stars
(red solid). The shaded regions indicate the $1\sigma$ interval around the median 
(i.e. the scatter between runs with different initial conditions and merger
histories). The MW (M31) GCS is shown in purple (magenta). We use the 
same bin sizes for the simulations as for the observations, explicitly shown for
the observed profiles.
